Computing astrophysical inferences with diffusive nested sampling

### 2014-01-31 ms.tex
MCMC is hard because
Random trivial work

Computing the consequences of a posterior distribution can be a challenging
task. Usually we want to marginalise out nuisance parameters, to compute
particular posterior probabilities such as $P(\theta > 1.5)$, or to summarise
the posterior distribution for easy communication with others.
Markov Chain Monte Carlo (MCMC) algorithms provide a general set of tools
for achieving these goals.

\section{Diffusive Nested Sampling}
DNS is essentially just the Metropolis algorithm. However, instead of the
target distribution being the posterior $p(\pars|\data)$, the algorithm
constructs and then samples a ``mixture of constrained priors'':

@@

\section{Reverberation Mapping}
Many objects in the universe are too distant to resolve, so we cannot simply
``see'' what is going on. Rather we must infer what is going on. Active Galactic
Nuclei (AGN) are a good example.

>>>>

Computing the consequences of a posterior distribution can be a challenging
task. Usually we want to marginalise out nuisance parameters, to compute
particular posterior probabilities such as $P(\theta > 1.5)$, or to summarise
the posterior distribution for easy communication with others.
Markov Chain Monte Carlo (MCMC) algorithms provide a general set of tools
for achieving these goals. However, many standard MCMC algorithms are not
capable of exploring complicated probability distributions in a reasonable time.
Problems often occur due to multimodality, strong dependencies, and phase
transitions.

\section{Nested sampling}
The key idea of Nested Sampling \citep{skilling} is that Bayesian computation
should start from the prior $\pi(\pars)$ and move through a sequence of
distributions that successively compress the prior volume by a constant factor
that is (approximately) known.

\subsection{MCMC inside nested sampling}

\section{Diffusive nested sampling}
Diffusive Nested Sampling (DNS) is an alternative to the use of MCMC inside of
standard Nested Sampling. DNS is essentially just the Metropolis algorithm.
However, instead of the
target distribution being the posterior $p(\pars|\data)$, the algorithm
constructs and then samples a ``mixture of constrained priors'':

@@

%\section{Reverberation Mapping}
%Many objects in the universe are too distant to resolve, so we cannot simply
%``see'' what is going on. Rather we must infer what is going on. Active Galactic
%Nuclei (AGN) are a good example.
